%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                         %
% PREFACE                                                 %
%                                                         %
% This file is part of a BSc Thesis Project. See the      %
% LICENSE file for more information about licensing.      %
%                                                         %
% Author:     Matteo Seclì <secli.matteo@gmail.com>       %
% A.Y.:       2014/2015                                   %
% URL:        https://github.com/matteosecli/QMC          %
%                                                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Preface}
%Write something in the preface. Who inspired this project, why, 
%when....just think about something to write here.

Here I am, finally, writing this very last project as the ending of three years of Physics at the University of Trento.

My interest in computing and programming is quite an old story; I still remember that, as a child, I spent a lot of time learning the DOS 6 and how to program in Pascal and JavaScript. This interest has grown over the years and it eventually led me to discover new languages and new problems to solve. I've developed my own projects about the most different varieties of subjects: from basic cryptography to audio/video streams, to web-based platforms, to more scientific challenges with Matlab or Mathematica.

Until one year ago, I had no chance to blend this passion with the primary interest of my life: Physics. But then I've been offered a one-year exchange program at the University of Oslo, and I immediately chose ``Computational Physics'' as an optional class. The course exceeded my best expectations, mainly thanks to the professor, Morten Hjorth-Jensen, who did a great job in passing on his passion to his students. I've always spoken freely to him about those sides of Physics I like the most: the state-of-the-art mathematical formulations, the fundamental laws, and the recently-discovered quantum world (thanks to the course in ``Quantum Mechanics'' at the University of Oslo). In particular the last one had a great impact on my life, since I decided to follow the ``quantum path'' for my coming master studies.

Since he was well aware of my interests and I asked his guide for a more complex project, professor Morten Hjorth-Jensen proposed me a project tailored on my passions: a simulation of quantum dots, developed via Monte Carlo methods. The project immediately draw my entire attention and I spent almost two months at programming and analyzing the results, trying to shape my simulator in a more extensible way that allows to run it even on different systems (e.g., atoms). Later I further extended the project with the help of professor Francesco Pederiva, who suggested me some additional reading material that gave me better insights about the world of quantum dots..

This thesis is the result of these months of work. I went through many difficult steps; non-working code, endless obscure ``segmentation fault'' errors, negative values for the kinetic energy (clearly, some sort black magic happening in the code), programming nights at the university (``because the night is dark and full of coffee''), and days spent trying to figure out the meaning of very bad-written articles.

In the end I survived this jungle, but it would haven't been possible without the help of many people that I want to thank. First of all I want to say a big thank to professor Morten Hjorth-Jensen, that inspired me so much that I've decided to take a quantum-oriented master course in Computational Physics. I also want to thank Jørgen Høgberget, that helped me a lot with the code and made my days happier by saying around random Italian words like ``mozzarella'' and ``gorgonzola'' with a terrible and funny accent. Last but not least, I want to thank all of my friends, my family and my grandparents, that supported me during these years even with hard sacrifices. A big thank also goes to all of my professors both at the University of Trento and at the University of Oslo, that helped and guided me up to this point. Thank you all!

\begin{flushright}
	{ \THauthor }
\end{flushright}
\begin{flushleft}
	{ \THplace, \THdate }
\end{flushleft}


